4d $\cN=1$

### 2019-11-14 6dsusy.tex
6d

The action of supersymmetry is given by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) - \frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  .
\end{align*}
where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
We point out some conventions in the definition of $I^{(2)}$. 
First, we define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
\[
\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
\]
Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
\[
(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
\]
The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}

@@

and
\begin{align*}
\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) - \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) .
\end{align*}

@@

Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
\begin{align*}
& - \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
\\ 
& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2
\end{align*}
By \label{prop:cliffordactionproperties} item (2), the first, second, fifth, and sixth terms combine to give
\[
- \frac{1}{2} \left( \sd \dd \rho(\Gamma(Q,\psi)) Q_2 + \sd \dd \rho(\Gamma(Q_2, \psi))Q_1 \right)  .
\]
This term is equal to $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2)) \psi$ by \ref{prop:3psi}. 
The Clifford relation implies this term cancels with the remaining terms.

>>>>

The action of supersymmetry is given by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) \textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
\end{align*}
where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
We point out some conventions in the definition of $I^{(2)}$. 
Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
\[
\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
\]
%Similarly, $\Gamma(\psi^*, \psi^*)_U \in V$ is defined as the image of $\psi^* \otimes \psi^*$ under the composition 
%\[
%(S_+ \otimes U) \otimes (S_+ \otimes U) \cong (S_+ \otimes S_+) \otimes (U \otimes U) \xto{\Gamma \otimes \omega_{U}} V .
%\]
%The pairing in the first term in $I^{(2)}$ is then induced from the natural one on $V$. 
%Also, $(Q_1, \psi^*)$ is defined as the image of $Q_1 \otimes \psi^*$ under the composition \brian{is this one zero???}

@@

and
\begin{align*}
\{S, I^{(2)}(Q_1,Q_2)\} = & \frac{1}{2} \Gamma(Q_1,Q_2) \Gamma(\psi^*, \sd \dd \psi) \textcolor{red}{- \frac{1}{2} (Q_1, \psi^*) (Q_2, \sd \dd \psi) - \frac{1}{2} (Q_1, \sd \dd \psi) (Q_2, \psi^*) }.
\end{align*}
Note that we can rewrite this as $\frac{1}{2} \rho(\Gamma(Q_1, Q_2)) \sd \dd \psi$.

@@

Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
\begin{align*}
& - \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
\\ 
& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
\end{align*}
By Proposition \ref{prop:cliffordactionproperties} item (2), the first, second, and fourth terms combine to give
\[
- \frac{1}{2} \left( \sd \dd \rho(\Gamma(Q,\psi)) Q_2 + \sd \dd \rho(\Gamma(Q_2, \psi))Q_1 \right)  .
\]
This term is equal to $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2)) \psi$ by \ref{prop:3psi}. 
The Clifford relation implies this term cancels with the remaining terms.
